drivers response diversity

### 2024-07-05 drivers_response_diversity.Rmd
tidied

```{r}
# packages relevant for data analysis
library(tidyverse)
library(here)
library(readr)
library(readxl)
library(gratia)
library(mgcv)
library(forcats)
library(ggpubr)
library(RColorBrewer)
library(broom)
library(grid)
library(DHARMa)
library(mgcViz)
library(gridExtra)
library(grid)

# function for the GAMs (old)
# source(here("function_GAM.R"))

# new function for temp and depth models 
source(here("function_temp_depth.R"))
```

@@

lm1_plot <- bind_model1 |> 
  ggplot(aes(sum_species, fit,  color = category, fill = category)) +
  geom_line(linewidth = 1.2) +
  geom_ribbon(aes(ymin = (fit - se.fit), ymax = (fit + se.fit)),  alpha = 0.3, color = NA) +
  theme_classic(base_size = 20) +
  ylab("Mean dissimilarity") +
  xlab("Species richness") +
  ylim(1,3) +
  scale_fill_manual(values = mycolor, aesthetics = c("color", "fill"), guide = NULL)

lm2_plot <- bind_model2 |> 
  ggplot(aes(Phos_max, fit, color = category, fill = category)) +
  geom_line(linewidth = 1.2) +
  geom_ribbon(aes(ymin = (fit - se.fit), ymax = (fit + se.fit)),  alpha = 0.3, color = NA) +
  theme_classic(base_size = 20) +
  ylab("Mean dissimilarity") +
  xlab("Maximum total phosphorus (µg/L)") +
  ylim(1,3) +
  scale_fill_manual(values = mycolor, aesthetics = c("color", "fill"), guide = NULL)

>>>>

```{r}
# packages relevant for data analysis
library(tidyverse)
library(here)
library(readr)
library(readxl)
library(gratia)
library(mgcv)
library(forcats)
library(ggpubr)
library(RColorBrewer)
library(broom)
library(grid)
library(DHARMa)
library(mgcViz)
library(gridExtra)
library(grid)
library(viridis)
```

@@

lm1_plot <- bind_model1 |> 
  ggplot(aes(sum_species, fit,  color = category, fill = category)) +
  geom_line(linewidth = 1.2) +
  geom_ribbon(aes(ymin = (fit - se.fit), ymax = (fit + se.fit)),  alpha = 0.3, color = NA) +
  theme_classic(base_size = 20) +
  ylab("Mean dissimilarity") +
  xlab("Species richness") +
  # ylim(1,3) +
  scale_fill_manual(values = mycolor, aesthetics = c("color", "fill"), guide = NULL)

lm2_plot <- bind_model2 |> 
  ggplot(aes(Phos_max, fit, color = category, fill = category)) +
  geom_line(linewidth = 1.2) +
  geom_ribbon(aes(ymin = (fit - se.fit), ymax = (fit + se.fit)),  alpha = 0.3, color = NA) +
  theme_classic(base_size = 20) +
  ylab("Mean dissimilarity") +
  xlab("Maximum total phosphorus (µg/L)") +
  # ylim(1,3) +
  scale_fill_manual(values = mycolor, aesthetics = c("color", "fill"), guide = NULL)
